Segmentation of Electron Microscopy Images for Connectomics

### 2018-05-02 papers/quals2018/5_proposed.tex
added proposal figure{

To further prevent this problem of undersegmentation, we will augment our current work to correct merge errors as well.
Generally, correcting merge errors is more difficult than correcting split errors because the space of possible split candidates grows quickly~\cite{parag2015properties}. 
However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
Consider Figure~\ref{fig:proposal} that shows an incorrectly merged segment consisting a few neurons.
We can extract a coarser skeleton from this segment that does not hit every spine but still gets the general shape.
In particular, it shows three main paths in this one segment.

Once locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
The surface separating the two segments is our ``split'' candidate.
We will extract a cubic region of interest around this candidate and input the region into our previously discussed merge classifier.
If the classifier suggests that the segments belong to one neuron, we will ignore the split candidate.
Otherwise we will divide this segment based on the candidate.
With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.

>>>>

To further prevent this problem of undersegmentation, we will augment our current work to correct merge errors as well.
Generally, correcting merge errors is more difficult than correcting split errors because the space of possible split candidates grows quickly~\cite{parag2015properties}. 
However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
Skeletons corresponding to undersegmented labels will have junctions at the failed merge (Fig.~\ref{fig:proposed}). 
This greatly reduces the search space and will enable correcting split errors in a fraction of the current time.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{./figures/split-proposal.png}
	\caption{An example where the input segmentation incorrectly merged two neurons together. The black circle indicates the junction from the skeletonized representation.}
	\label{fig:proposal}
\end{figure}

After locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
This watershed algorithm will provide two seeds on opposite sides of the discovered junction.
The surface separating the two segments is our ``split'' candidate.
We will extract a cubic region of interest around this candidate and input the region into our previously discussed merge classifier.
If the classifier suggests that the segments belong to one neuron, we will ignore the split candidate.
Otherwise we will divide this segment based on the candidate.
With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.
This process will run recursively for a given segment in case more than two neurons are improperly merged.
